Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-09-18 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x paper

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych,
      apaTables,
      rstatix )

@@

### Perform Exploratory Factor Analysis (EFA)
```{r sri_efa, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

sri <- sri %>% 
  group_by(ID) %>% 
  summarise(mean_disrup = mean(disruption_appraisal),
            mean_confi = mean(confidence_appraisal)
  ) %>% 
  dplyr::select(mean_disrup,
                mean_confi)

# Perform exploratory factor analysis (EFA) with 2 factors
sri_efa_result <- fa(sri, 
                     nfactors = 2, 
                     rotate = "varimax"
                     )

# Display the result
print(sri_efa_result)

sri_efa_result$communality
print(sri_efa_result$loadings, cutoff = 0.4)

# Cronbach's Alpha
alpha((sri), check.keys =TRUE)

@@

### Prevalence Rating as manipulation check
```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

############## Prevalence Rating as manipulation check #########################

sri.preva.table <-
  sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

# insert a table into HTML
knitr::kable(sri.preva.table,
             caption = "Prevalence rating")

#### with event 
sri.preva.event.table <-
  sri %>%
  group_by(ID, event) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

# insert a table into HTML
knitr::kable(sri.preva.event.table,
             caption = "Prevalence rating with events")

# create a new data frame with rating
sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))

# plotting prevalence rating for groups
preva_group_plot <- 
  sri_preva %>% 
  mutate(ID = factor(ID,
                     levels = c("Novice",
                                "Expert"
                                )
                     )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = prevalence_rating)) +
  geom_boxplot(mapping = aes(fill = ID),
               outlier.shape = NA) +
  geom_point(size = 1,
             alpha = 0.4,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  scale_x_discrete(limits = c("Novice", "Expert")) +
  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
  labs(x = "",
       y = "Prevalence Rating") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("How widespread is this event in the classroom?") +
  theme_cowplot()

preva_group_plot

@@

# select relevant columns --> only subject ID and mean 
df_sjt <- df_sjt %>%
  dplyr::select(UI06_05, # ID
         SJT_AL_gek, # Monitoring
         SJT_ST_gek, # Managing momentum
         SJT_R_gek, # Rules and routines
         SJT_KF_gek) %>% # All
  filter(!UI06_05 == 201) # exclude ID with no eye tracking data

# remove NAs
df_sjt <- na.omit(df_sjt)

# rename columns
df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
                           "Monitoring" = "SJT_AL_gek",
                           "Managing momentum" = "SJT_ST_gek",
                           "Rules and routines" = "SJT_R_gek",
                           "All" = "SJT_KF_gek"))

# changing from wide to long format
df_sjt_long <- df_sjt %>% 
  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")

@@

# define expert and novice with ifelse function in wide format
df_sjt$Group = ifelse(df_sjt$Group < 200, "Novice","Expert")

#### ALL #### 
# t-test for expertise differences 
t.test(x = df_sjt$All[df_sjt$Group == "Expert"],
       y = df_sjt$All[df_sjt$Group == "Novice"],
       var.equal = TRUE)

# effect size for expertise differences
d_sjt_all <- CohenD(x = df_sjt$All[df_sjt$Group == "Expert"],
                    y = df_sjt$All[df_sjt$Group == "Novice"],
                    na.rm = TRUE
                    )

@@

#### MANAGING MOMENTUM #### 
# t-test for expertise differences 
t.test(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
       y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_mm <- CohenD(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
                   y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
                   na.rm = TRUE
                  )

@@

#### MONITORING ####
# t-test for expertise differences 
t.test(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
       y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_moni <- CohenD(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
                     y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
                     na.rm = TRUE
                    )

@@

#### RULES & ROUTINES #### 
# t-test for expertise differences 
t.test(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
       y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"],
       var.equal = TRUE
      )

# effect size for expertise differences
d_sjt_rr <- CohenD(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
                   y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"],
                   na.rm = TRUE
                  )

@@

@@

>>>>

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych,
      apaTables,
      rstatix,
      MBESS)

@@

### Internal consistency (Omega) for disruption and confidence appraisal
```{r sri_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

# change long to wide format
sri_wide <- sri %>%
  pivot_wider(names_from = event, 
              values_from = c(disruption_appraisal, confidence_appraisal, prevalence_rating))

### DISRUPTIONS APPRAISAL

# create new data frame with only disruption items
sri_wide_disrup <- sri_wide %>%
  dplyr::select(starts_with("disruption_appraisal")) %>% 
  drop_na()

# calculate omega with omega() function  
omega_disrup <- omega(sri_wide_disrup)

# display the results 
print(omega_disrup)

### CONFIDENCE APPRAISAL

# create new data frame with only confidence items
sri_wide_confi <- sri_wide %>%
  dplyr::select(starts_with("confidence_appraisal")) %>% 
  drop_na()

# calculate omega with omega() function  
omega_confi <- omega(sri_wide_confi)

# display the results 
print(omega_confi)

@@

### Prevalence Rating as manipulation check
```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# 
# ############## Prevalence Rating as manipulation check #########################
# 
# sri.preva.table <-
#   sri %>%
#   group_by(ID) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.table,
#              caption = "Prevalence rating")
# 
# #### with event 
# sri.preva.event.table <-
#   sri %>%
#   group_by(ID, event) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.event.table,
#              caption = "Prevalence rating with events")
# 
# # create a new data frame with rating
# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
# 
# # plotting prevalence rating for groups
# preva_group_plot <- 
#   sri_preva %>% 
#   mutate(ID = factor(ID,
#                      levels = c("Novice",
#                                 "Expert"
#                                 )
#                      )
#          ) %>% 
#   ggplot(mapping = aes(x = ID,
#                        y = prevalence_rating)) +
#   geom_boxplot(mapping = aes(fill = ID),
#                outlier.shape = NA) +
#   geom_point(size = 1,
#              alpha = 0.4,
#              position = position_jitter(seed = 1,
#                                         width = 0.1,
#                                         height = 0.1)) +
#   scale_x_discrete(limits = c("Novice", "Expert")) +
#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
#   labs(x = "",
#        y = "Prevalence Rating") + 
#   scale_fill_brewer(palette  = "RdBu") +  
#   ggtitle("How widespread is this event in the classroom?") +
#   theme_cowplot()
# 
# preva_group_plot

@@

# select relevant columns --> only subject ID and mean 
df_sjt_mean <- df_sjt %>%
  dplyr::select(UI06_05, # ID
         SJT_AL_gek, # Monitoring
         SJT_ST_gek, # Managing momentum
         SJT_R_gek, # Rules and routines
         SJT_KF_gek) %>% # All
  filter(!UI06_05 == 201) # exclude ID with no eye tracking data

# remove NAs
df_sjt <- na.omit(df_sjt_mean)

# rename columns
df_sjt_mean <- rename(df_sjt_mean, c("Group" = "UI06_05",
                           "Monitoring" = "SJT_AL_gek",
                           "Managing momentum" = "SJT_ST_gek",
                           "Rules and routines" = "SJT_R_gek",
                           "All" = "SJT_KF_gek"))

# changing from wide to long format
df_sjt_long <- df_sjt_mean %>% 
  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")

@@

# define expert and novice with ifelse function in wide format
df_sjt_mean$Group = ifelse(df_sjt_mean$Group < 200, "Novice","Expert")

#### ALL #### 
# t-test for expertise differences 
t.test(x = df_sjt_mean$All[df_sjt_mean$Group == "Expert"],
       y = df_sjt_mean$All[df_sjt_mean$Group == "Novice"],
       var.equal = TRUE)

# effect size for expertise differences
d_sjt_all <- CohenD(x = df_sjt_mean$All[df_sjt_mean$Group == "Expert"],
                    y = df_sjt_mean$All[df_sjt_mean$Group == "Novice"],
                    na.rm = TRUE
                    )

@@

#### MANAGING MOMENTUM #### 
# t-test for expertise differences 
t.test(x = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Expert"],
       y = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_mm <- CohenD(x = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Expert"],
                   y = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Novice"],
                   na.rm = TRUE
                  )

@@

#### MONITORING ####
# t-test for expertise differences 
t.test(x = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Expert"],
       y = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_moni <- CohenD(x = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Expert"],
                     y = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Novice"],
                     na.rm = TRUE
                    )

@@

#### RULES & ROUTINES #### 
# t-test for expertise differences 
t.test(x = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Expert"],
       y = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Novice"],
       var.equal = TRUE
      )

# effect size for expertise differences
d_sjt_rr <- CohenD(x = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Expert"],
                   y = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Novice"],
                   na.rm = TRUE
                  )

@@

### Internal consistency (Omega) for SJT
```{r sjt_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

### MANAGING MOMENTUM

# select relevant columns
df_sjt_mm <- df_sjt %>%
    dplyr::select(WT_S1_F1F2_AL:WT_S4_F4F6_AL)

# remove NAs
df_sjt_mm <- na.omit(df_sjt_mm)

# calculate omega with omega() function  
omega_sjt_mm <- omega(df_sjt_mm)

# display the results 
print(omega_sjt_mm)

### MONITORING

# select relevant columns
df_sjt_m <- df_sjt %>%
    dplyr::select(WT_S5_F1F2_ST:WT_S9_F4F5_ST)

# remove NAs
df_sjt_m <- na.omit(df_sjt_m)

# calculate omega with omega() function  
omega_sjt_m <- omega(df_sjt_m)

# display the results 
print(omega_sjt_m)

### RULES & ROUTINES

# select relevant columns
df_sjt_r <- df_sjt %>%
  dplyr::select(WT_S11_F1F5_R:WT_S14_F4F6_R)

# remove NAs
df_sjt_r <- na.omit(df_sjt_r)

# calculate omega with omega() function  
omega_sjt_r <- omega(df_sjt_r)

# display the results 
print(omega_sjt_r)

@@

### Internal consistency (Omega) for Classroom Questionnaire
```{r cm_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# read in data
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LM01_01:LM01_08, # classroom management 
                LP01_01:LP01_08) # non- & paraverbal communication

### CLASSROOM MANAGEMENT

# select relevant columns
df_quest_cm <- df_quest %>%
    dplyr::select(LM01_01:LM01_08)

# remove NAs
df_quest_cm <- na.omit(df_quest_cm)

# calculate omega with omega() function  
omega_quest_cm <- omega(df_quest_cm)

# display the results 
print(omega_quest_cm)

### NON- & PARAVERBAL COMMUNICATION

# select relevant columns
df_quest_npvc <- df_quest %>%
    dplyr::select(LP01_01:LP01_08)

# remove NAs
df_quest_npvc <- na.omit(df_quest_npvc)

# calculate omega with omega() function  
omega_quest_npvc <- omega(df_quest_npvc)

# display the results 
print(omega_quest_npvc)
